---
title: "TCGA assembler- full GBM download."
output: html_notebook
author: "Sam Lee"
lab: "McConnell Lab group"
date: "01/09/17"
---

Using TCGA Assembler to download GBM RNASeq data from TCGA. This is collaborative work with Varun. We will download and create a count table as well as downloading clinical data for all the samples.

### Parameters

```{r}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(downloader))
out.dir <- "/home/slee/outputs/2017-09-02-tcga-gbm-count-tables"
```

## Get patient IDs

```{r}
url <- "https://raw.githubusercontent.com/VarunSVenkatesh/VarunStorage/master/TCGAGBMcaseslist.csv"
filename <- "TCGAGBMcaseslist.csv"
if (!file.exists(filename)) download(url,filename)

TCGAGBMcases <- read_tsv(filename)

caseIDs <- pull(TCGAGBMcases, CaseID)
head(caseIDs)

```


## TCGA download

source the modules

```{r}
tcgaDir <- "/home/mmclab/downloads/TCGA-Assembler"
setwd(tcgaDir)

source("Module_A.R")
source("Module_B.R")

```



## Non-normalised count data download

Downlaod count data for the caseID patients.

```{r}
DownloadRNASeqData(cancerType = "GBM",
                   assayPlatform = "gene_RNAseq",
                   inputPatientIDs = caseIDs,
                   saveFolderName = file.path(out.dir, "module_1")
)
```

Process the downlaoded file to get a count table with HGNC gene-ids and RSEM generated counts + z-scores for each patient sample

## CHECK CODE BEFORE RUNNING

```{r}
raw_count.list <-ProcessRNASeqData(
  inputFilePath = list.files(file.path(out.dir, "module_1"), full.names = T)[1],
										outputFileName = paste("all-cases",
																					 sep = "__"),
										dataType = "geneExp",
										outputFileFolder = file.path(out.dir, "gene_expr")
)

```

```{r}
hgnc.list.raw <- as.character(as.data.frame(raw_count.list[[2]])$GeneSymbol)

gbm.raw.tbl <- as.data.frame(raw_count.list[[1]]) %>%
  mutate(gene_name = hgnc.list.raw) %>%
  filter(gene_name != "?")

```

Next we want to extract the raw-count columns and the gene name columns from the total table (that incldues the z-scores (tau score??))

```{r}
gbm.count.tbl <- select(gbm.raw.tbl, - ends_with(".1")) %>%
  select(gene_name, starts_with("TCGA"))

```

Save this count table.

```{r}
write_csv(
  gbm.count.tbl,
  file.path(out.dir, "tcga-rsem-count-table-gene-level.csv"),
  col_names = TRUE
)

```

## Clinical data

Download the clinical data for patients as well 

```{r}
DownloadBiospecimenClinicalData(
  "GBM",
  saveFolderName = file.path(out.dir, "clinical-data") 
)

```

This is the data all downloaded. The clinical info will require further processing when it needs to be used for grouping etc but this is all the data downloaded. Before the count can be used it needs to be normalised for sample size. 

This info is then copied into a place where it can be acessed in a read format by all users of the server. This is `/tcga/gbm/`

```{bash, eval=F}
if [ ! -d /tcga/gbm ]
then
    sudo mkdir -p /tcga/gbm
fi

sudo cp -r /home/slee/outputs/2017-09-02-tcga-gbm-count-tables/* /tcga/gbm

```