---
title: "TCGA assembler- full GBM download."
output: html_notebook
author: "Sam Lee"
lab: "McConnell Lab group"
date: "01/09/17"
---

Using TCGA Assembler to download GBM RNASeq data from TCGA. This Is collaborative work with Varun.

### Parameters

```{r}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(downloader))
out.dir <- "/home/slee/outputs/2017-09-02-tcga-gbm-count-tables"
```

## Get patient IDs

```{r}
url <- "https://raw.githubusercontent.com/VarunSVenkatesh/VarunStorage/master/TCGAGBMcaseslist.csv"
filename <- "TCGAGBMcaseslist.csv"
if (!file.exists(filename)) download(url,filename)

TCGAGBMcases <- read_tsv(filename)

caseIDs <- pull(TCGAGBMcases, CaseID)
head(caseIDs)

```


## TCGA download

source the modules

```{r}
tcgaDir <- "/home/mmclab/downloads/TCGA-Assembler"
setwd(tcgaDir)

source("Module_A.R")
source("Module_B.R")

```



## Non-normalised count data download

Downlaod count data for the caseID patients.

```{r}
DownloadRNASeqData(cancerType = "GBM",
                   assayPlatform = "gene_RNAseq",
                   inputPatientIDs = caseIDs,
                   saveFolderName = file.path(out.dir, "module_1")
)
```

Process the downlaoded file to get a count table with HGNC gene-ids and RSEM generated counts + z-scores for each patient sample

## CHECK CODE BEFORE RUNNING

```{r}
raw_count.list <-ProcessRNASeqData(
  inputFilePath = list.files(file.path(out.dir, "module_1"), full.names = T)[1],
										outputFileName = paste("all-cases",
																					 sep = "__"),
										dataType = "geneExp",
										outputFileFolder = file.path(out.dir, "gene_expr")
)

```

```{r}
hgnc.list.raw <- as.character(as.data.frame(raw_count.list[[2]])$GeneSymbol)

gbm.count.tbl <- as.data.frame(raw_count.list[[1]]) %>%
  mutate(gene_name = hgnc.list.raw) %>%
  filter(gene_name != "?")

```

Save count table as CSV

## Clinical data

Download the clinical data for patients as well 

```{r}

```